SPECS-decadal-MOS

### 2017-08-10 SPECS/specs-decade-mos.Rmd
SPECS MOS R-script

library(esd)
#library(knitr)
#purl('git/esd_Rmarkdown/SPECS/specs-decade-mos.Rmd', output='git/esd_Rmarkdown/SPECS/specs-decade-mos.R')
#library(ncdf)
setwd("~/R")
experiments <- c('~/data/gfdl_DECA.rda','~/data/hadcm3_DECA.rda','~/data/miroc5_DECA.rda','~/data/mpi_DECA.rda')

@@

## Test to examine the link between large-scale temperature and wet-day mean precip
## Derive the saturation vapour pressure from temperature
## retrieve did not get the right time stamp:
  es <- annual(C.C.eq(retrieve('~/Downloads/air.mon.mean.nc',lon=c(-60,40),lat=c(20,70))))
  es.eof <- EOF(mask(es,land=TRUE))

## Also get the mean sea-level pressure for the wet-day frequency 
  slp <- annual(retrieve('~/Downloads/slp.mon.mean.nc',lon=c(-60,40),lat=c(20,70)))
  slp.eof <- EOF(slp)

@@

for (iexp in 1:1) {
  print(paste('Get the decadal predictors saved locally in',experiments[iexp]))
  load(experiments[iexp])

## Leave-one-out cross-validation experiments
## Names of file names with results stored  
fw1name <- paste('specsdecadal.z.fw.y1.gcm',iexp,'rda',sep='.')
mu1name <- paste('specsdecadal.z.mu.y1.gcm',iexp,'rda',sep='.')
fw3name <- paste('specsdecadal.z.fw.y1.3.gcm',iexp,'rda',sep='.')
mu3name <- paste('specsdecadal.z.mu.y1.3.gcm',iexp,'rda',sep='.')
fw5name <- paste('specsdecadal.z.fw.y1.5.gcm',iexp,'rda',sep='.')
mu5name <- paste('specsdecadal.z.mu.y1.5.gcm',iexp,'rda',sep='.')
fw9name <- paste('specsdecadal.z.fw.y1.9.gcm',iexp,'rda',sep='.')
mu9name <- paste('specsdecadal.z.mu.y1.9.gcm',iexp,'rda',sep='.')

>>>>

library(esd)
#library(knitr)
#purl('~/git/esd_Rmarkdown/SPECS/specs-decade-mos.Rmd', output='~/git/esd_Rmarkdown/SPECS/specs-decade-mos.R')
#library(ncdf)
setwd("~/R")
experiments <- c('~/data/gfdl_DECA.rda','~/data/hadcm3_DECA.rda','~/data/miroc5_DECA.rda','~/data/mpi_DECA.rda')

@@

## Test to examine the link between large-scale temperature and wet-day mean precip
## Derive the saturation vapour pressure from temperature
## retrieve did not get the right time stamp:
  es <- annual(C.C.eq(retrieve('~/Downloads/air.mon.mean.nc',lon=c(-60,40),lat=c(20,70))))
  index(es) <- year(es)
  es.eof <- EOF(mask(es,land=TRUE))

## Also get the mean sea-level pressure for the wet-day frequency 
  slp <- annual(retrieve('~/Downloads/slp.mon.mean.nc',lon=c(-60,40),lat=c(20,70)))
  index(slp) <- year(slp)
  slp.eof <- EOF(slp)

@@

for (iexp in 1:1) {
  print(paste('Get the decadal predictors saved locally in',experiments[iexp]))
  load(experiments[iexp])
  dir <- substr(experiments[iexp],1,nchar(experiments[iexp])-4)
  if (!file.exists(dir)) dir.create(dir)

## Leave-one-out cross-validation experiments
## Names of file names with results stored  
fw1name <- paste(dir,'/specsdecadal.z.fw.y1.gcm.',iexp,'rda',sep='')
mu1name <- paste(dir,'/specsdecadal.z.mu.y1.gcm.',iexp,'rda',sep='')
fw3name <- paste(dir,'/specsdecadal.z.fw.y1.3.gcm.',iexp,'rda',sep='')
mu3name <- paste(dir,'/specsdecadal.z.mu.y1.3.gcm.',iexp,'rda',sep='')
fw5name <- paste(dir,'/specsdecadal.z.fw.y1.5.gcm.',iexp,'rda',sep='')
mu5name <- paste(dir,'/specsdecadal.z.mu.y1.5.gcm.',iexp,'rda',sep='')
fw9name <- paste(dir,'/specsdecadal.z.fw.y1.9.gcm.',iexp,'rda',sep='')
mu9name <- paste(dir,'/specsdecadal.z.mu.y1.9.gcm.',iexp,'rda',sep='')
